---
title: "codeBook"
output: 
    html_document:
        keep_md: true
    
---
#code book

##For each record it is provided:


* Triaxial acceleration from the accelerometer (total acceleration) and the estimated body acceleration.
* Triaxial Angular velocity from the gyroscope. 
* A 561-feature vector with time and frequency domain variables. 
* Its activity label. 
* An identifier of the subject who carried out the experiment.

##The dataset includes the following files:

* 'README.txt'

* 'features_info.txt': Shows information about the variables used on the feature vector.

* 'features.txt': List of all features.

* 'activity_labels.txt': Links the class labels with their activity name.

* 'train/X_train.txt': Training set.

* 'train/y_train.txt': Training labels.

* 'test/X_test.txt': Test set.

* 'test/y_test.txt': Test labels.


##sIGNAL PATTERN      
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

tBodyAcc-XYZ
tGravityAcc-XYZ
tBodyAccJerk-XYZ
tBodyGyro-XYZ
tBodyGyroJerk-XYZ
tBodyAccMag
tGravityAccMag
tBodyAccJerkMag
tBodyGyroMag
tBodyGyroJerkMag
fBodyAcc-XYZ
fBodyAccJerk-XYZ
fBodyGyro-XYZ
fBodyAccMag
fBodyAccJerkMag
fBodyGyroMag
fBodyGyroJerkMag


The set of variables that were estimated from these signals are: 

mean(): Mean value
std(): Standard deviation
mad(): Median absolute deviation 
max(): Largest value in array
min(): Smallest value in array
sma(): Signal magnitude area
energy(): Energy measure. Sum of the squares divided by the number of values. 
iqr(): Interquartile range 
entropy(): Signal entropy
arCoeff(): Autorregresion coefficients with Burg order equal to 4
correlation(): correlation coefficient between two signals
maxInds(): index of the frequency component with largest magnitude
meanFreq(): Weighted average of the frequency components to obtain a mean frequency
skewness(): skewness of the frequency domain signal 
kurtosis(): kurtosis of the frequency domain signal 
bandsEnergy(): Energy of a frequency interval within the 64 bins of the FFT of each window.
angle(): Angle between to vectors.

##COMPUTATIONS
```{r loadData, cache=TRUE}
library(dplyr)


setwd("C:/Users/Joanna/Desktop/coursera tidy data/assessment")
testData <- read.table("./UCI HAR Dataset/test/X_test.txt", quote="\"")
testData_act <- read.table("./UCI HAR Dataset/test/y_test.txt", quote="\"")
testData_sub <- read.table("./UCI HAR Dataset/test/subject_test.txt",header=FALSE)
trainData  <- read.table("./UCI HAR Dataset/train/X_train.txt", quote="\"")
trainData_act <- read.table("./UCI HAR Dataset/train/y_train.txt",header=FALSE)
trainData_sub <- read.table("./UCI HAR Dataset/train/subject_train.txt",header=FALSE)

features <- read.table("./UCI HAR Dataset/features.txt", quote="\"")
activity_labels <- read.table("./UCI HAR Dataset/activity_labels.txt", quote="\"", colClasses="character")

```

##PART 1

```{r part1, cache=TRUE}
#merged data sets
#Merges the training and the test sets to create one data set.
testData2<-cbind(testData, testData_act, testData_sub)
trainData2<-cbind(trainData, trainData_act, trainData_sub)

complete<-rbind(testData, trainData)
complete2<-rbind(testData2, trainData2)


features[,2]<-as.character(features[,2])
colnames(complete)<-features[,2]

```
##PART 2

```{r part2, cache=TRUE}
#Extracts only the measurements on the mean and standard deviation for each measurement
set1<-select(complete, contains("mean()"))
set2<-select(complete, contains("std()"))
set<-cbind(set1,set2)


```
##PART 3

```{r part3, cache=TRUE}
#Uses descriptive activity names to name the activities in the data set
testData_act$V1 <- factor(testData_act$V1,levels=activity_labels$V1,labels=activity_labels$V2)
trainData_act$V1 <- factor(trainData_act$V1,levels=activity_labels$V1,labels=activity_labels$V2)
head(testData_act)
```

##PART 4

```{r part4, cache=TRUE}
#Appropriately labels the data set with descriptive variable names. 
colnames(testData)<-colnames(trainData)<-colnames(complete)<-features[,2]
colnames(testData_act)<-colnames(trainData_act)<-c("Activity")
colnames(testData_sub)<-colnames(trainData_sub)<-c("Subject")

```

##PART 5

```{r part5, cache=TRUE}
#From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
